---
title: "rRINEX Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rRINEX-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# rRINEX: get started!  


## RTKLIB

Upon loading the library , the user will be asked to specify the path were RTKLIB bin folder is located in the machine running R.  

It is strongly advised that you install  [RTKLIB](http://www.rtklib.com){target=_blank} to use all of the functionalities of rRINEX.  


```{r setup }
#library(lattice)
library(tmap) 
library(rRINEX)
```

### Example data  

The reference to some example  RINEX files.  

```{r loadData}
ef<-rRINEX::paths.to.example.files()
print(ef)
```

### Get approximate  position of survey from RINEX file  

Get and plot the approximate position of the survey using the 
RINEX observation file. 
NB: --- *not* all RINEX observation files have this information.

```{r getinfo}
info<-rRINEX::getInfoFromRINEX.OBS.header(ef$obs.rover)
print(info)
```


### Get position of closest base stations to survey  

Get and plot the approximate position of the survey using the 
RINEX observation file. 
NB: --- *not* all RINEX observation files have this information.

```{r getbs}
rinex.info<- rRINEX::getInfoFromRINEX.OBS.header(ef$obs.rover)

point<- sf::st_sfc(sf::st_point(rinex.info$latlong), crs = 9000)

sf.close<-rRINEX::getClosestStations(ef$obs.rover)

tmap::tmap_mode("view")
tmap::tm_shape(sf.close) +
    tmap::tm_symbols(col="blue", scale=.99) +
tmap::tm_shape(point) +
    tmap::tm_symbols(col="red", scale=1.5)
```

## Which base stations are used?  

You  have two choices, Italy's stations, or EUREF. Below is an example plotting both

```{r, out.width="100%" }
tmap::tmap_mode("view")
tmap::tm_shape(rRINEX::stazioniGNSS$IGSNetwork) +
    tmap::tm_dots(col="blue" ) +
tmap::tm_shape(rRINEX::stazioniGNSS$ITA) +
    tmap::tm_dots(col="red") 
```
