---
title: "rRINEX Get Started!"
output: 
  rmarkdown::html_vignette:
    keep_md: true 
    toc: true
self_contained: no
vignette: >
  %\VignetteIndexEntry{rRINEX-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc} 
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = T, fig.width=6, fig.height=3,
  comment = "#>"
) 
```
  
## Get started  

You  have two choices, Italy's CORS stations, or EUREF CORS stations.  
Below is an example plotting both in red and blue respectively.


```{r  message=F, out.width="100%" }



```


## RTKLIB

Upon loading the library , the user will be asked to specify the path were RTKLIB bin folder is located in the machine running R.  

It is strongly advised that you install  [RTKLIB](http://www.rtklib.com){target=_blank} to use all of the functionalities of rRINEX.  


```{r setup }
#library(lattice)
#library(tmap) 
library(rRINEX)
```

### Example data  

The reference to some example  RINEX files.  

```{r  message=F}
ef<-rRINEX::paths.to.example.files()
ef<-"/archivio/cirgeoGNSSrinex_bot/Download/189140783_M__data_20201211_105001.zip"
print(ef)
```

### Get and plot approximate  position of survey from RINEX file  

Get and plot the approximate position of the survey using the 
RINEX observation file.   

NB: --- *not* all RINEX observation files have this information.

```{r  message=F}
ef.dec<-decompress(ef)
ef<-list(obs.rover=ef.dec)
info<- rRINEX::getApproxPositionFromRINEX.OBS.header(ef$obs.rover)
print(sprintf("Long. %f and Lat. %f ", info[[1]], info[[2]] ) ) 
## Window buffer in degrees
buffer<-0.001
# area <- get_stamenmap(bbox = c(left = info[[1]] - buffer, bottom =info[[2]] - buffer, 
#                                   right = info[[1]]+buffer, top = info[[2]] + buffer), zoom=14)
#  
```


### Get position of closest base stations to survey  

Get and plot the approximate position of the survey using the 
RINEX observation file.   

NB: --- *not* all RINEX observation files have this information.

```{r comment=F, message=F, warning=F }
rinex.info<- rRINEX::getInfoFromRINEX.OBS.header(ef$obs.rover)
getFile.Veneto(rinex.info$timestamp, "XXXX")
point<- sf::st_sfc(sf::st_point(rinex.info$latlong), crs = 9000)

sf.close<-rRINEX::getClosestStations(ef$obs.rover)
 
 tmap::tmap_mode("view")
 tmap::tm_shape(sf.close) +
     tmap::tm_symbols(col="blue", scale=.99) +
 tmap::tm_shape(point) +
     tmap::tm_symbols(col="red", scale=1.5)
```
